Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-16 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community of web services, Goals:        
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Facilitate Web Service Discovery over Internet}.
            \item \textbf{Maintaining high reputation and market share}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

\begin{itemize}
    \item \textbf{How can we model the
        community of agent-based services in order to maximize the utility
        of involved users, web services and community organizers?}
        \begin{itemize}
            \item Most of the recent work on communities of
            services are either user-centric and focus on user satisfaction
            or system-centric and focus on the whole system throughput, performance and utilization.
        \end{itemize}

    \item \textbf{How can we model fair and stable communities as coalitions
        of agent-based web services?}
        \begin{itemize}
            \item All parties involved are self-interest agents and have the authority to deviate leave the community if they can improve their income in some other ways.
        \end{itemize}

@@

\begin{frame}{Continue: Problems and Research Questions}
 \begin{itemize}
   \item \textbf{How can we model and analyze the cooperation
        among the community members in realistic, applicable and practical
        settings?}
        \begin{itemize}
            \item Modeling the preference and valuation functions considering the worth of all subsets of players in realistic cooperative scenarios
            \item Solution concepts complexity issues            
        \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Communities of Web Services}
    \begin{frame}{Community of Web Services}
        Communities of Web Services
        \begin{itemize}
            \item Ease and improve the process of Web services discovery in an open environment like the Internet
        	\item Improve service quality, availability and responsiveness
            \item Maintaining high reputation and market share
        \end{itemize}

        \begin{figure}[htbp]
            \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
        \end{figure}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Social commitments in MASs}
    \begin{frame}{Communities of Web Services}
        Communities of Web Services
        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Communities of web services operations}
            \begin{itemize}
              \item Community Development
              \item Web Services Attraction and Retention
              \item Web Service Selection
            \end{itemize}                      	      	
        \end{itemize}

        \begin{figure}[htbp]
            \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
        \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \begin{frame}{Cooperative Game Theory}
      \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
         \begin{itemize}
            \item A set of tasks needs to be performed, they require different expertise.
            \item Agents do not have enough resource on their own to perform a task.
            \item Find complementary agents to perform the tasks.
            \begin{itemize}
                \item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
                \item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
            \end{itemize}
        \end{itemize}
        \item \textbf{Issues:}
            \begin{itemize}
                \item What coalition to form?
                \item How to reward each each member when a task is completed?
            \end{itemize}
      \end{itemize}
    \end{frame}

@@

    \begin{itemize}
        \item \textbf{Problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
        \item \textbf{Solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Transferable and Non Transferable Utility Games}
    \begin{itemize}
        \item \textbf{Games with Transferable Utility (TU games)}
        \begin{itemize}
            \item Utility is worth the same for all agents
            \item Utility can be {\color{red} compared} or {\color{red} transfered} between agents.
            \item Irrespective of the division of the coalitional payoff, members of the coalition enjoy the same total utility.
        \end{itemize}

        \begin{definition} [Valuation or Characteristic function]\label{dfn:valuationfunction}
            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
        \end{definition}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties of valuation functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{red} additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{red} super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{red} weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
        \item {\color{red} subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{red} convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution properties}
    Let $x \in R^n$ be a solution of the TU game $(N,v)$
    \begin{itemize}
        \item {\color{red} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{red} Efficiency:} $x(N) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
        \end{itemize}
        \item {\color{red} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff
        \end{itemize}
        \item {\color{red} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item A condition for a coalition to form:
            {\color{red}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
        \item The {\color{red} core} is a stability concepts for which no agents prefer to deviate to form a different coalition.
        \item Is the coalition stable $\Leftrightarrow$ Is the core non-empty
    \end{itemize}
\end{frame}

@@

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Concepts: Shapley Value}
    \begin{definition} [Marginal contribution]\label{dfn:marginalcontribution}
        The {\color{red}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
    \end{definition}

    \begin{itemize}
        \item By considering average marginal contribution over all possible subset of coalitions, we can achieve a fair distribution.\\
        \item Let $\prod(N)$ denote the set of all permutations of the sequence $(1,...n)$. Therefore: $\phi_i(N,v) = \frac{\sum_{\sigma \in \phi_i(N)}}{mc(\sigma)}$
    \end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services created high competition and great business opportunities for online service developers
        \item Community of web services: Clustering similar web services in order to:
        \begin{itemize}
            \item \textbf{Provide better user satisfaction through high availability and responsiveness}.
            \item \textbf{Facilitate Web Service Discovery over Internet}.
            \item \textbf{Maintain high reputation and market share}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsection{Communities of Web Services}
%    \begin{frame}{Community of Web Services}
%       Communities of Web Services
%       \begin{itemize}
%           \item Ease and improve the process of Web services discovery in an open environment like the Internet
%       	\item Improve service quality, availability and responsiveness
%           \item Maintaining high reputation and market share
%       \end{itemize}

%       \begin{figure}[htbp]
%           \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
%           \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
%       \end{figure}

%   \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Social commitments in MASs}
    \begin{frame}{Communities of Web Services}
        Communities of Web Services
        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Communities of web services operations}
            \begin{itemize}
              \item Community development
              \item Web services attraction and retention
              \item Web service selection
            \end{itemize}                      	      	
        \end{itemize}

        \begin{figure}[htbp]
            \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
        \end{figure}
    \end{frame}

\begin{frame}{Problems and Research Questions}

\begin{itemize}
    \item \textbf{How can we model the
        community of agent-based services in order to maximize the utility
        of involved users, web services and community organizers?}
        \begin{itemize}
            \item Most of the work on communities of
            services are either user-centric and focus on user satisfaction
            or system-centric and focus on the whole system throughput, performance and utilization.
        \end{itemize}

    \item \textbf{How can we model fair and stable communities as coalitions
        of agent-based web services?}
        \begin{itemize}
            \item All parties involved are self-interest agents and have the right to leave the community if they can improve their income in some other ways.
        \end{itemize}

@@

\begin{frame}{Continue: Problems and Research Questions}
 \begin{itemize}
   \item \textbf{How can we model and analyze the cooperation
        among the community members in realistic, applicable and practical
        settings?}
        \begin{itemize}
            \item The first issue is about the evaluation of web services that are working together inside communities.
            \item The second issue is about the complexity of cooperative game theory solution concepts.
        \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \begin{frame}{Cooperative Game Theory}
      \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
         \begin{itemize}
            \item Cooperation to perform a set of tasks that requires different expertise.
            \item Agents do not have enough resource on their own to perform the tasks.
            \item Examples:
            \begin{itemize}
                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
            \end{itemize}
        \end{itemize}
        \item \textbf{Issues:}
            \begin{itemize}
                \item Coalition formation.
                \item Rewarding members when a task is completed.
            \end{itemize}
      \end{itemize}
    \end{frame}

@@

    \begin{itemize}
        \item \textbf{Problem:} Given a game $(N,v)$, and assuming all agents in $N$ want to cooperate, how to distribute the gain among the agents?
        \item \textbf{Solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Transferable and Non Transferable Utility Games}
    \begin{itemize}
        \item \textbf{Games with Transferable Utility (TU games)}
        \begin{itemize}
            \item Utility is worth the same for all agents
            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
            \item Irrespective of the division of the coalitional payoff.
            \begin{itemize}
                \item In that case members of the coalition enjoy the same total utility.
            \end{itemize}
        \end{itemize}

        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
        \end{definition}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties of Valuation Functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{blue} Additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{blue} Super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$        
    \end{itemize}

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
    \begin{itemize}
        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Properties}
    Let $x \in R^n$ be a solution of the TU game $(N,v)$
    \begin{itemize}
        \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{blue} Efficiency:} $x(N) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
        \end{itemize}
        \item {\color{blue} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff
        \end{itemize}
        \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item A condition for a coalition to form:
            {\color{blue}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
        \item The {\color{blue} core} is a stability concept for which no agents prefer to deviate to form a different coalition.        
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
       \item The coalition is stable $\Leftrightarrow$ The core is not empty
    \end{itemize}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Concepts: Shapley Value}
    \begin{definition} [Marginal Contribution]\label{dfn:marginalcontribution}
        The {\color{red}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
    \end{definition}

    \begin{itemize}
        \item By considering average marginal contribution over all possible subsets of coalitions, we can achieve a fair distribution.\\
        \item Let $\prod(N)$ denote the set of all permutations of the sequence $(1,...n)$. Therefore: $\phi_i(N,v) = \frac{\sum_{\sigma \in \phi_i(N)}}{mc(\sigma)}$
    \end{itemize}
